Estimating nucleon substructure properties in a\\[.2ex] unified hydrodynamic model of p-Pb and Pb-Pb collisions

### 2018-04-13 talk/qm2018.tex
Add some content to paper on trento
Add some more content to the talk

\begin{frame}[t]{\scshape Heavy-ion collision model}
  \centering
  \medskip
  \begin{tikzpicture}
    \node (a) {\includegraphics{hannah_collision}};
    \node[align=left, anchor=north west] at (a.north west) {%
      \scriptsize Figure: H. Petersen, MADAI
      };
  \end{tikzpicture}
  \begin{columns}[T]
    \begin{column}{0.3\textwidth}
      \texttt{\scshape\color{theme} TrENTo} {\small initial conditions}\\
      \smallskip\hrule\medskip
      {\scriptsize parametric entropy deposition}\\
      {\tiny \color{theme}PRC.92.011901}\\[2ex]
      \texttt{\scshape\color{theme} freestream} {\small pre-flow}\\
      \smallskip\hrule\medskip
      {\scriptsize infinitely weak coupling limit}\\
      {\tiny \color{theme} PRC.91.064906, ~PRC.80.034902}
    \end{column}
    \hfill
    \begin{column}{0.3\textwidth}
      \texttt{\scshape\color{theme} VISH2+1} {\small viscous hydro}\\
      \smallskip\hrule\medskip
      {\scriptsize 14-mom.\ approx w/ shear \& bulk}\\
      {\tiny \color{theme} PRC.77.064901, ~J.CPC.2015.08.039}\\[2ex]
      \texttt{\scshape\color{theme}frzout} {\small sampler}\\
      \smallskip\hrule\medskip
      {\scriptsize non-RTA shear \& bulk corrections}\\
      {\tiny\color{theme} J.E.\ Bernhard thesis}
    \end{column}
    \hfill
    \begin{column}{0.3\textwidth}
      \texttt{\scshape\color{theme} UrQMD} {\small Boltzmann cascade}
      \smallskip\hrule\medskip
      {\scriptsize hadronic afterburner, simulate scatterings and decays}\\
      {\tiny\color{theme} PPNP.98.00058, ~JPG.25.9.308}\\[2ex]
      {\scriptsize Final observables calculated as similar as possible to experiment}
    \end{column}
  \end{columns}
  \begin{tikzpicture}[overlay]
    \draw (-3, -.2) -- (-2.7, -.2);
    \draw (-2.7, -.2) -- (-2.7, 3.6);
    \draw (-2.7, 3.6) -- (-2.4, 3.6);
    \draw (2.4, -.2) -- (2.7, -.2);
    \draw (2.7, -.2) -- (2.7, 3.6);
    \draw (2.7, 3.6) -- (3.0, 3.6);
  \end{tikzpicture}
\end{frame}

@@

\begin{frame}[b, plain]{\scshape Parameter estimates from lead-lead collisions}
  \begin{columns}[b]
    \begin{column}{.4\textwidth}
      \begin{tikzpicture}
        \node (A) {\includegraphics<1>[height=.82\textheight]{observables_design}};
        \node (B) {\includegraphics<2>[height=.82\textheight]{observables_posterior}};
        \node [xshift=2.8cm, yshift=3.2cm, rotate=-45] {%
          \textcolor{theme}{\scshape New!}%
          };
      \end{tikzpicture}
    \end{column}
    \begin{column}{.02\textwidth}
    \end{column}
    \begin{column}{.55\textwidth}
      \begin{itemize}
        \item Combined analysis of 2.76 and 5.02 TeV beam energies
        \item Parametric initial conditions and medium parameters
        \item See thesis by Jonah Bernhard {\small [\url{99999}]}
      \end{itemize}
      \begin{tikzpicture}
        \node (0, 0) {\includegraphics<1>{region_shear_blank}};
        \node (0, 0) {\includegraphics<2>{region_shear}};
        \node [xshift=.3cm, yshift=.6cm] {\only<1>{\fontsize{80}{0}\selectfont \color{theme!30} ?}};
        \node [xshift=3cm, yshift=1.8cm, rotate=-45] {%
          \textcolor{theme}{\scshape New!}%
          };
      \end{tikzpicture}
    \end{column}
  \end{columns}
  \medskip
\end{frame}

@@

\begin{frame}[t]{\scshape Nuclear structure}
  \begin{columns}[T]
    \begin{column}{.4\textwidth}
      \begin{figure}
        \includegraphics[width=.9\columnwidth]{lead_208}
        \caption{Pb$^{208}$ nucleus}
      \end{figure}
    \end{column}
    \begin{column}{.6\textwidth}
      \bigskip
      \textcolor{theme}{Original \trento\ model:}
      \begin{itemize}
        \item Sample nucleon radii from spherical or deformed Woods-Saxon distributions
        \item Euler angles resampled to preserve minimum nucleon distance
          $d_\mathrm{min}$ [fm]
        \item Gaussian nucleons of width $w$ [fm]
      \end{itemize}
      \medskip
      \textcolor{theme}{This work:}
      \begin{itemize}
        \item Trade Gaussian nucleon for lumpy nucleon
      \end{itemize}
      \begin{tikzpicture}[absolute, overlay]
        \node (a) at (2, -.75) {\includegraphics[scale=.5]{proton}};
        \node[right=of a.east] (b) {\includegraphics[scale=.5]{proton_partons}};
        \draw[->, thick] (a) -- (b);
      \end{tikzpicture}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}[t]{\scshape Cross sections}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics{trento_model_part}\\
        \small MC-Glauber cross sections\\
        (proton d.o.f. shown)
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \centering \bigskip
      \textcolor{theme}{Original \trento\ model:}
      \begin{align*}
        P_\text{coll} &= 1 - \exp[-\sigma_{gg} T_{pp}(b)] \\
        \sigma_\text{nn}^\text{inel} &= \int 2\pi b\, db\, P_\text{coll}(b)
      \end{align*}
      \only<1>{\includegraphics<1>[scale=.8]{collision_profile}}
      \only<2>{
        \textcolor{theme}{This work:}
        \begin{equation*}
          P_\text{coll} \rightarrow 1 - \prod_{i,j=1}^{n_\text{part}}
          [1 - P_\text{coll}(b_{ij})]
        \end{equation*}
        Solve for opacity parameter $\sigma_{gg}$ numerically
      }
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]{\scshape Participant thickness functions}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics{trento_model_thickness}
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \centering \bigskip
      \textcolor{theme}{Original \trento\ model:}
      \begin{equation*}
        T_\text{nucleus}(x, y) = \sum\limits_{i=1}^{N_\text{part}}
        \gamma_i\, T_\text{proton}(x - x_i, y - y_i)
      \end{equation*}
      {\small Random weight $\gamma_i$ sampled from Gamma distribution with unit mean
      and variance $1/k$.}\\[2ex]
      \textcolor{theme}{This work:}
      \begin{equation*}
        \gamma_i\, T_\text{proton} \rightarrow \sum\limits_{j=1}^{N_\text{parton}}
        \gamma_j\,T_\text{parton} 
      \end{equation*}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]{\scshape Entropy deposition}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics{trento_model_entropy}
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \bigskip \centering
      \textcolor{theme}{Generalized Mean Ansatz:}
      \begin{equation*}
        \frac{dS}{d\eta} \propto T_R(T_A, T_B) \equiv
        \left(\frac{T_A^p + T_B^p}{2}\right)^{1/p}
      \end{equation*}
      \begin{equation*}
        \small
        T_R =
        \begin{cases}
          \max(T_A, T_B) & p \rightarrow +\infty, \\[.5ex]
          (T_A + T_B)/2 & p = +1, \\[.5ex]
          \sqrt{T_A T_B} & p = 0, \\[.5ex]
          2\, T_A T_B/(T_A + T_B) & p = -1, \\[.5ex]
          \min(T_A, T_B) & p \rightarrow -\infty.
        \end{cases}
      \end{equation*}
      \smallskip
      \begin{center}
        \small $T$ denotes \emph{participant} thickness function
      \end{center}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]{\scshape Free streaming}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics{trento_model_freestream}\\
        \small arrows: fluid velocity\\weighted by energy density
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \bigskip \centering
      \textcolor{theme}{Pre-equillibrium phase:}
      \begin{itemize}
        \small
        \item Massless non-interacting parton gas matched to viscous hydrodynamics
          \textcolor{theme}{\scriptsize PRC.91.064906, PRC.80.034902}.
        \item Must reinterpret initial entropy density as initial gluon density,\,
          $dN_g/y \sim dS/dy$
        \item Initialize hydro with non-zero $u^\mu$ and $\pi^{\mu\nu}$
      \end{itemize}
      \medskip
      \includegraphics{coupling}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}[t]{\scshape Computer experiment design}
  \bigskip
  \begin{columns}[T]
    \begin{column}{.55\textwidth}
      \scriptsize
      \begin{tabular}{lll}
        Parameter         & Description                        & Range           \\
        \paddedhline
        Norm              & Overall normalization              & 12--28          \\
        $p$               & Entropy deposition parameter       & $-1$ to $+1$    \\
        $\sigmaf$         & Relative parton fluct. std.\       & 0--2            \\
        $w$               & Parton sampling radius             & 0.4--1.2 fm     \\
        $\X$              & Parton structure parameter         & 0--1            \\
        $\npartons$       & Number of partons                  & 1--10           \\
        $\dmin$           & Nucleon exclusion volume           & 0--4.9 fm$^3$   \\
        $\tau_{fs}$       & Free streaming time                & 0.1--1.5 fm/$c$ \\
        $\eta/s$ min      & Shear viscosity at $T_c$           & 0--0.2          \\
        $\eta/s$ slope    & Slope above $T_c$                  & 0--8 GeV$^{-1}$ \\
        $\eta/s$ crv      & Curvature above $T_c$              & $-1$ to $1$     \\
        $\zeta/s$ norm    & Bulk viscosity peak height         & 0--0.1          \\
        $\zeta/s$ width   & Bulk viscosity peak width          & 0--0.1 GeV      \\
        $\zeta/s$ temp    & Bulk viscosity peak location       & 150--200 MeV    \\
        $T_\text{switch}$ & Particlization temperature         & 135--165 MeV    \\
      \end{tabular}
    \end{column}
    \begin{column}{.45\textwidth}
      \textcolor{theme}{\scshape Important details:}
      \smallskip
      \begin{itemize}
        \small
        \item Parton width is reparametrized:\\[1ex]
          $v = v_\text{min} + \X(v_\text{max} - v_\text{min})$\\[1ex]
          $v_\text{min} = 0.2$~fm,~ $v_\text{max} = w$\\[1ex]
        \item Parton sampling radius is \emph{not} equivalent to the proton radius
          in the proton c.o.m.\ frame, e.g.\ see\\
          \textcolor{theme}{\scriptsize PRC.94.024919}\\[1ex]
        \item Other parameters same as Pb+Pb analysis at 2.76 and 5.02 TeV
      \end{itemize}
    \end{column}
  \end{columns}
  \begin{center}
    \color{theme}
    500 design points per collision system, $\mathcal{O}(10^4)$ events per design point!
  \end{center}
\end{frame}

\begin{frame}[plain]
  \begin{tikzpicture}[remember picture, overlay]
    \node[anchor=west] at (current page.west) {
      \includegraphics[height=.95\paperheight]{observables_design}
      };
    \node[anchor=east] at (current page.east) {
      \includegraphics[height=.95\paperheight]{observables_design}
      };
    \draw[<-] (current page.center) ++(-.75, 1.7) --
      node[above] {\footnotesize Prior}
      node[below] {\tiny (training data)}
      ++(1.5, 0);
    \draw[->] (current page.center) ++(-.75, -1.2) --
      node[above] {\footnotesize Posterior}
      node[below] {\tiny (samples)}
      ++(1.5, 0);
  \end{tikzpicture}
\end{frame}

\begin{frame}[plain]
  \begin{tikzpicture}
    \node {\includegraphics[height=\textheight]{posterior}};
    \node (title) at (6.5, 3.5) {\color{theme}{\scshape \Large Bayesian posterior}};
    \node<1-2>[draw=none, text width=7cm, align=left, below=.2cm of title] (b1) {%
      One row (column) for each parameter
      };
    \node<1-2>[draw=none, text width=7cm, align=left, below=.2cm of b1] (b2) {%
      Diagonal panels: marginal distribution of a single model parameter
      };
    \node<1-2>[draw=none, text width=7cm, align=left, below=.2cm of b2] (b3) {%
      Off-diagonal panels: joint distribution between a pair of model parameters
      };
    \node<2>[draw=none, text width=7cm, align=left, below=.4cm of b3] (b4) {%
      Let's zoom in on some specific regions...
      };
    \draw<1-2>[->, thick, theme] (b2.west) to [out=180, in=90] (-.3, 1.2);
    \draw<1-2>[->, thick, theme] (b3.west) to [out=180, in=90] (.2, -.5);
    \node<3>[xshift=.5cm, yshift=-.5cm, scale=.3] {\includegraphics{magnifying-glass}};
    \node<4>[xshift=-.5cm, yshift=-1cm, scale=.3] {\includegraphics{magnifying-glass}};
  \end{tikzpicture}
\end{frame}

\begin{frame}{\scshape Maximum a posteriori parameters}

>>>>

\begin{frame}[t]{\scshape Heavy-ion collision model}
  \centering
  \medskip
  \begin{tikzpicture}
    \node (a) {\includegraphics[width=.95\textwidth]{hannah_collision}};
    \node[align=left, anchor=north west] at (a.north west) {%
      \scriptsize Figure: H. Petersen, MADAI
      };
  \end{tikzpicture}
  \begin{columns}[T]
    \begin{column}{0.3\textwidth}
      \texttt{\scshape\color{theme} TrENTo} {\small initial conditions}\\
      \smallskip\hrule\medskip
      {\scriptsize parametric entropy deposition}\\
      {\tiny \color{theme}PRC.92.011901}\\[2ex]
      \texttt{\scshape\color{theme} freestream} {\small pre-flow}\\
      \smallskip\hrule\medskip
      {\scriptsize infinitely weak coupling limit}\\
      {\tiny \color{theme} PRC.91.064906, ~PRC.80.034902}
    \end{column}
    \hfill
    \begin{column}{0.3\textwidth}
      \texttt{\scshape\color{theme} VISH2+1} {\small viscous hydro}\\
      \smallskip\hrule\medskip
      {\scriptsize 14-mom.\ approx w/ shear \& bulk}\\
      {\tiny \color{theme} PRC.77.064901, ~J.CPC.2015.08.039}\\[2ex]
      \texttt{\scshape\color{theme}frzout} {\small sampler}\\
      \smallskip\hrule\medskip
      {\scriptsize non-RTA shear \& bulk corrections}\\
      {\tiny\color{theme} J.E.\ Bernhard thesis}
    \end{column}
    \hfill
    \begin{column}{0.3\textwidth}
      \texttt{\scshape\color{theme} UrQMD} {\small Boltzmann cascade}
      \smallskip\hrule\medskip
      {\scriptsize hadronic afterburner, simulate scatterings and decays}\\
      {\tiny\color{theme} PPNP.98.00058, ~JPG.25.9.308}\\[2ex]
      {\scriptsize Final observables calculated as similar as possible to experiment}
    \end{column}
  \end{columns}
  \begin{tikzpicture}[overlay]
    \draw (-3, -.2) -- (-2.7, -.2);
    \draw (-2.7, -.2) -- (-2.7, 3.6);
    \draw (-2.7, 3.6) -- (-2.4, 3.6);
    \draw (2.4, -.2) -- (2.7, -.2);
    \draw (2.7, -.2) -- (2.7, 3.6);
    \draw (2.7, 3.6) -- (3.0, 3.6);
  \end{tikzpicture}
\end{frame}

@@

\begin{frame}[b, plain]{\scshape Parameter estimates from lead-lead collisions}
  \begin{columns}[b]
    \begin{column}{.43\textwidth}
      \includegraphics<1>[width=\textwidth]{lead_observables_design}
      \includegraphics<2>[width=\textwidth]{lead_observables_posterior}
    \end{column}
    \begin{column}{.57\textwidth}
      \begin{itemize}
        \item Combined analysis of 2.76 and 5.02
          TeV beam energies \textcolor{theme}{\scshape (New!)} 
        \item Parametric initial conditions and medium parameters\
        \item Quantitative estimates on $\eta/s$ and $\zeta/s$ with meaningful uncertainties
        \item See thesis by Jonah Bernhard {\small [\url{99999}]}
      \end{itemize}
      \bigskip
      \includegraphics<1>[width=\textwidth]{region_shear_bulk}
      \includegraphics<2>[width=\textwidth]{region_shear_bulk}
    \end{column}
  \end{columns}
  \medskip
\end{frame}

@@

\begin{frame}[t]{\scshape Nuclear structure}
  \begin{columns}[T]
    \begin{column}{.4\textwidth}
      \begin{figure}
        \includegraphics[width=.9\columnwidth]{pb208}\\
        Pb$^{208}$ nucleus
      \end{figure}
    \end{column}
    \begin{column}{.6\textwidth}
      \bigskip
      \textcolor{theme}{Original \trento\ model:}
      \begin{itemize}
        \item Sample nucleon radii from spherical or deformed Woods-Saxon distributions
        \item Euler angles resampled to preserve minimum nucleon distance
          $d_\mathrm{min}$ [fm]
        \item Gaussian nucleons of width $w$ [fm]
      \end{itemize}
      \medskip
      \textcolor{theme}{This work:}
      \begin{itemize}
        \item Trade Gaussian nucleon for lumpy nucleon
      \end{itemize}
      \begin{tikzpicture}[absolute, overlay]
        \node (a) at (2, -.75) {\includegraphics[scale=.5]{proton}};
        \node[right=of a.east] (b) {\includegraphics[scale=.5]{proton_partons}};
        \draw[->, thick] (a) -- (b);
      \end{tikzpicture}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}[t]{\scshape Cross sections}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{trento_model_part}\\
        \small MC-Glauber cross sections\\
        (proton d.o.f. shown)
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \centering \bigskip
      \textcolor{theme}{Original \trento\ model:}
      \begin{align*}
        P_\text{coll} &= 1 - \exp[-\sigma_{gg} T_{pp}(b)] \\
        \sigma_\text{nn}^\text{inel} &= \int 2\pi b\, db\, P_\text{coll}(b)
      \end{align*}
      \only<1>{\includegraphics<1>[scale=.8]{collision_profile}}
      \only<2>{
        \textcolor{theme}{This work:}
        \begin{equation*}
          P_\text{coll} \rightarrow 1 - \prod_{i,j=1}^{n_\text{part}}
          [1 - P_\text{coll}(b_{ij})]
        \end{equation*}
        Solve for opacity parameter $\sigma_{gg}$ numerically
      }
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]{\scshape Participant thickness functions}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{trento_model_thickness}
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \centering \bigskip
      \textcolor{theme}{Original \trento\ model:}
      \begin{equation*}
        T_\text{nucleus}(x, y) = \sum\limits_{i=1}^{N_\text{part}}
        \gamma_i\, T_\text{proton}(x - x_i, y - y_i)
      \end{equation*}
      {\small Random weight $\gamma_i$ sampled from Gamma distribution with unit mean
      and variance $1/k$.}\\[2ex]
      \textcolor{theme}{This work:}
      \begin{equation*}
        \gamma_i\, T_\text{proton} \rightarrow \sum\limits_{j=1}^{N_\text{parton}}
        \gamma_j\,T_\text{parton} 
      \end{equation*}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]{\scshape Entropy deposition}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{trento_model_entropy}
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \bigskip \centering
      \textcolor{theme}{Generalized Mean Ansatz:}
      \begin{equation*}
        \frac{dS}{d\eta} \propto T_R(T_A, T_B) \equiv
        \left(\frac{T_A^p + T_B^p}{2}\right)^{1/p}
      \end{equation*}
      \begin{equation*}
        T_R =
        \begin{cases}
          \max(T_A, T_B) & p \rightarrow +\infty, \\[.5ex]
          (T_A + T_B)/2 & p = +1, \\[.5ex]
          \sqrt{T_A T_B} & p = 0, \\[.5ex]
          2\, T_A T_B/(T_A + T_B) & p = -1, \\[.5ex]
          \min(T_A, T_B) & p \rightarrow -\infty.
        \end{cases}
      \end{equation*}
      \smallskip
      \begin{center}
        \small $T$ denotes \emph{participant} thickness function
      \end{center}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]{\scshape Free streaming}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{trento_model_freestream}\\
        \small arrows: fluid velocity\\weighted by energy density
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \bigskip \centering
      \textcolor{theme}{Pre-equillibrium phase:}
      \begin{itemize}
        \small
        \item Massless non-interacting parton gas matched to viscous hydrodynamics
          \textcolor{theme}{\scriptsize PRC.91.064906, PRC.80.034902}.
        \item Must reinterpret initial entropy density as initial gluon density,\,
          $dN_g/y \sim dS/dy$
        \item Initialize hydro with non-zero $u^\mu$ and $\pi^{\mu\nu}$
      \end{itemize}
      \medskip
      \includegraphics{coupling}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}[t]{\scshape Computer experiment design}
  \bigskip
  \begin{columns}[T]
    \begin{column}{.6\textwidth}
      \scriptsize
      \begin{tabular}{lll}
        Parameter         & Description                        & Range           \\
        \paddedhline
        Norm              & Overall normalization              & 12--28          \\
        $p$               & Entropy deposition parameter       & $-1$ to $+1$    \\
        $\sigmaf$         & Relative parton fluct. std.\       & 0--2            \\
        $w$               & Parton sampling radius             & 0.4--1.2 fm     \\
        $\X$              & Parton structure parameter         & 0--1            \\
        $\npartons$       & Number of partons                  & 1--10           \\
        $\dmin$           & Nucleon exclusion volume           & 0--4.9 fm$^3$   \\
        $\tau_{fs}$       & Free streaming time                & 0.1--1.5 fm/$c$ \\
        $\eta/s$ min      & Shear viscosity at $T_c$           & 0--0.2          \\
        $\eta/s$ slope    & Slope above $T_c$                  & 0--8 GeV$^{-1}$ \\
        $\eta/s$ crv      & Curvature above $T_c$              & $-1$ to $1$     \\
        $\zeta/s$ norm    & Bulk viscosity peak height         & 0--0.1          \\
        $\zeta/s$ width   & Bulk viscosity peak width          & 0--0.1 GeV      \\
        $\zeta/s$ temp    & Bulk viscosity peak location       & 150--200 MeV    \\
        $T_\text{switch}$ & Particlization temperature         & 135--165 MeV    \\
      \end{tabular}
    \end{column}
    \begin{column}{.4\textwidth}
      \textcolor{theme}{\scshape Important details:}
      \smallskip
      \begin{itemize}
        \small
        \item Parton width reparametrized:\\[1ex]
          $v = v_\text{min} + \X(v_\text{max} - v_\text{min})$\\[1ex]
          $v_\text{min} = 0.2$~fm,~ $v_\text{max} = w$\\[1ex]
        \item Parton sampling radius is \emph{not} equivalent to the proton radius
          in the proton c.o.m.\ frame, see\\
          \textcolor{theme}{\scriptsize PRC.94.024919}\\[1ex]
        \item Other parameters same as combined Pb+Pb analysis at 2.76 and 5.02 TeV
      \end{itemize}
    \end{column}
  \end{columns}
  \begin{center}
    \color{theme}
    500 design points per collision system, $\mathcal{O}(10^4)$ events per design point!
  \end{center}
\end{frame}

\begin{frame}[plain]
  \begin{tikzpicture}[remember picture, overlay]
    \node[anchor=west] at (current page.west) {
      \includegraphics[height=.95\paperheight]{observables_design}
      };
    \node[anchor=east] at (current page.east) {
      \includegraphics[height=.95\paperheight]{observables_posterior}
      };
    \draw[<-] (current page.center) ++(-.75, 1.7) --
      node[above] {\footnotesize Prior}
      node[below] {\tiny (training data)}
      ++(1.5, 0);
    \draw[->] (current page.center) ++(-.75, -1.2) --
      node[above] {\footnotesize Posterior}
      node[below] {\tiny (samples)}
      ++(1.5, 0);
  \end{tikzpicture}
\end{frame}

\begin{frame}[plain]
  \begin{tikzpicture}
    \node {\includegraphics[height=.98\paperheight]{posterior}};
    \node (title) at (6.0, 3.5) {\color{theme}{\scshape \Large Bayesian posterior}};
    \node<1-2>[draw=none, text width=6.5cm, align=left, below=.2cm of title] (b1) {%
      \small One row (column) for each parameter
      };
    \node<1-2>[draw=none, text width=6.5cm, align=left, below=.1cm of b1] (b2) {%
      \small Diagonal panels: marginal distribution of a single model parameter
      };
    \node<1-2>[draw=none, text width=6.5cm, align=left, below=.1cm of b2] (b3) {%
      \small Off-diagonal panels: joint distribution between a pair of model parameters
      };
    \node<2>[draw=none, text width=6.5cm, align=left, below=.2cm of b3] (b4) {%
      \textcolor{theme}{Let's look at some specific regions...}
      };
    \draw<1-2>[->, thick, theme] (b2.west) to [out=180, in=90] (-.58, 1.3);
    \draw<1-2>[->, thick, theme] (b3.west) to [out=180, in=90] (-.05, 0);
    \node<3>[xshift=-2.8cm, yshift=3.2cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<4>[xshift=-1.2cm, yshift=1.6cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<5>[xshift=-.7cm, yshift=1.1cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
  \end{tikzpicture}
\end{frame}

\begin{frame}{\scshape Maximum a posteriori parameters}
  \includegraphics[height=.8\textheight]{find_map}
\end{frame}
